---
output:
  md_document:
    variant: gfm
---

[![img](https://img.shields.io/badge/Lifecycle-Experimental-339999)](https://github.com/bcgov/repomountie/blob/master/doc/lifecycle-badges.md)

# simsbc

*simsbc* provides access to biodiversity data and projects from British Columbia's Species Inventory Management System (SIMS).

SIMS is a web application for managing, submitting, and accessing biodiversity data in British Columbia. It is designed for biologists working for or in partnership with the Province, supporting relationships between government, industry, Indigenous communities, and consultants to advance natural resource stewardship.

The *simsbc* R package complements the web application by loading SIMS data directly into R, removing the need to import and export intermediate files and enabling real-time dashboards and analytics.

```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/"
)
library(simsbc)
```

### Installation

You can install *simsbc* from GitHub using the [remotes](https://cran.r-project.org/package=remotes) package.
```{r eval = F}
install.packages("remotes")

# Install the simsbc package from GitHub
remotes::install_github("bcgov/simsbc")

library(simsbc)
```

### Usage

- (Get data)[https://bcgov.github.io/simsbc/articles/get_data.html]

### Roadmap

We are building rapidly towards letting biologists import species observations to SIMS, after which we will build functions for retrieving species observations.

### Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/bcgov/simsbc/issues/).

### How to Contribute

If you would like to contribute to the package, please see our 
[CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

### License

```
Copyright 2023 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the &quot;License&quot;);
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an &quot;AS IS&quot; BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
```

---
*This project was created using the [bcgovr](https://github.com/bcgov/bcgovr) package.* 
