---
title: "Introduction to simsbc"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{simsbc}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

*simsbc* aims to make your ecological data more accessible. You can load species observations and other data into a dataframe without needing to export and import intermediate files.

## Getting Access

If you aren't already a SIMS user, you can start by [submitting an access request](https://sims.nrs.gov.bc.ca). Your access request will only be approved if it is clear that you will be managing ecological data in British Columbia.

We are working on a separate, public-facing application for users who simply want to obtain data from other biologists' projects.

## Installation

After receiving access, you can install *simsbc* from GitHub using the [remotes](https://cran.r-project.org/package=remotes) package.
```{r eval = F}
# Run only once to be able to install packages from GitHub
install.packages("remotes")

# Run only once to use simsbc, or whenever you want to get the latest changes
remotes::install_github("bcgov/simsbc")

# Run every time you start R
library(simsbc)
```

We expect to release new features frequently. To use any newly built functions, you must reinstall *simsbc* from GitHub.

Some functions may break unexpectedly as we make frequent improvements to existing code, so we recommend not relying exclusively on *simsbc* until we announce our first proper release.

## Usage

We have tutorials for many common use cases:

- (Get data)[get_data.html]

## Contributing

All contributions are valuable and ideas are just as important as code!

### Ideas

If you have ideas for useful functions or improvements, please contact macgregor.aubertin-young@gov.bc.ca. Hearing your ideas will also help us prioritize what to build next.

### Code

If you want to contribute code, please see our [CONTRIBUTING](https://github.com/bcgov/simsbc/blob/main/CONTRIBUTING.md) guidelines.

If you work in the Natural Resource Ministries and want to contribute code but are not sure where to start, please contact macgregor.aubertin-young@gov.bc.ca. We would love to help you get started!
